On the combination of Set Functions and Failures

### 2014-01-31 docs/src/usage.tex
safe mode improved

@@

\item[\fbox{\code{ghc $opts$}}]\pindex{ghc}
Define additional options passed to the Glasgow Haskell Compiler (GHC)
when the generated Haskell programs are compiled.
One has to be careful when using such options.
For instance, in a global installation of \CYS
(see Section~\ref{sec-install}), libraries are pre-compiled
so that inconsistencies might occur if compilation options
might be changed.

>>>>

\item[\fbox{\code{+/-safe}}]\pindex{safe}
Turn on/off the safe execution mode.
In the safe execution mode, the initial goal is
not allowed to be of type \code{IO} and the program should not
import the module \code{Unsafe}.
Furthermore, the allowed commands are
\code{eval}, \code{load}, \code{quit}, and \code{reload}.
This mode is useful to use \CYS in uncontrolled environments,
like a computation service in a web page.

@@

\item[\fbox{\code{ghc $opts$}}]\pindex{ghc}
Define additional options passed to the Glasgow Haskell Compiler (GHC)
when the generated Haskell programs are compiled.
Many options necessary to compile Curry programs
are already set (you can see them by setting the verbosity
level to 2 or greater).
One has to be careful when providing additional options.
For instance, in a global installation of \CYS
(see Section~\ref{sec-install}), libraries are pre-compiled
so that inconsistencies might occur if compilation options
might be changed.
